dynamics

### 2023-03-01 scripts/workshop/dynamics.Rmd
update date
add code folding
knit it

---
title: "dynamics"
author: "Daniel Suh"
date: "2023-02-15"
output: html_document
---

@@

```{r}
library(tidyverse)
library(magrittr)
#install_github("thomasp85/patchwork")
library(patchwork)
library(ggnewscale)
library(here)
library(deSolve)
```

>>>>

---
title: "dynamics"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
---

@@

```{r, message = F}
library(tidyverse)
library(magrittr)
#install_github("thomasp85/patchwork")
library(patchwork)
library(ggnewscale)
library(here)
library(deSolve)
```
